Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-19 egpaper_supp.tex
in progress

\section{3D Object Dataset}
\label{sect:3dobject}
We run our ensemble of NZ-WHO templates as a detector on 3D Object dataset\cite{savarese07} and present detection average precision, average viewpoint precision, viewpoint confusion matrix and mean precision in pose estimation. See Fig.~\ref{fig:3dobject_ap}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
  (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
  (b) Bicycle
\caption{Detection and pose estimation on 3D Object dataset car category. (left) Average Precision (AP) and Average Viewpoint Precision (AVP) and (right) Viewpoint confusion table and MPPE, Viewpoint index 1 is front, 2 is front-right, 5 is back and 8 is front-left. Most of the error in viewpoint estimation come from frontal and back views}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_ap}
\end{figure}

More qualitative results are on the Fig.~\ref{fig:3dobject_good} and Fig.~\ref{fig:3dobject_bad}. The each of the template in the ensemble of NZ-WHO templates has a corresponding rendering and a CAD model. These can be transferred as a metadata and overlay the rendering on top of the detection.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car26.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car10.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle11.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car8.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car31.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} \\
  \hline
  Car & Bicycle \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset car and bike classes. In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car30.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} \\
  \hline
  Car & Bicycle \\
  \hline
  \end{tabular}
\caption{Failed pose estimation results on 3D Object dataset car and bike classes. In each column, original image (left) and detection result overlaid on top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bad}
\end{figure*}

>>>>

\section{3D Object Dataset}
\label{sect:3dobject}
We run our ensemble of NZ-WHO templates as a detector on 3D Object
dataset\cite{savarese07} without tuning and present detection average precision, average
viewpoint precision, viewpoint confusion matrix and mean precision in pose
estimation. See Fig.~\ref{fig:3dobject_ap}

Most of the error in viewpoint estimation come from frontal and back views

\begin{figure}[h]
  \centering
  \includegraphics[width=0.99\linewidth]{supp/car_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (a) Car\\
  \includegraphics[width=0.99\linewidth]{supp/bicycle_ap_3dobject_tight.png}\\
  \vspace{-5pt}
    (b) Bicycle\\
  \caption{Detection and pose estimation on 3D Object dataset car category (top) and bicycle category (bottom).
  Average Precision (red) and Average Viewpoint Precision (green) (left)
  Viewpoint confusion table and MPPE (right), Viewpoint index 1 is front, index 2 is
  front-right, \dots index 8 is front-left. }
  \label{fig:3dobject_ap}
\end{figure}

We put successful car detection results on Fig.~\ref{fig:3dobject_car_good} and
failure cases on Fig.~\ref{fig:3dobject_car_bad}. And for bicycle, successful
bicycle detection results are on Fig.~\ref{fig:3dobject_bicycle_good} and
failure cases on Fig.~\ref{fig:3dobject_bicycle_bad}.

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car32.png} &
  \includegraphics[width=0.40\linewidth]{supp/car26.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car29.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car10.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car1.png} &
  \includegraphics[width=0.40\linewidth]{supp/car8.png} \\
  \includegraphics[width=0.40\linewidth]{supp/car20.png} & 
  \includegraphics[width=0.40\linewidth]{supp/car31.png} \\
%   \includegraphics[width=0.40\linewidth]{supp/car33.png} & 
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset car
category. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/bicycle17.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle18.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle13.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle9.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle16.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle12.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle15.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle10.png} \\
  \hline
  \end{tabular}
\caption{Successful detection results on 3D Object dataset car
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
  \hline
  \includegraphics[width=0.40\linewidth]{supp/car13.png} &
  \includegraphics[width=0.40\linewidth]{supp/car30.png} \\ 
  \includegraphics[width=0.40\linewidth]{supp/car18.png} &
  \includegraphics[width=0.40\linewidth]{supp/car25.png} \\
  \hline
  \end{tabular}
\caption{Failed pose estimation results on 3D Object dataset car and bike
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|c|c|}
\hline 
  \includegraphics[width=0.40\linewidth]{supp/bicycle1.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle5.png} \\
  \includegraphics[width=0.40\linewidth]{supp/bicycle19.png} &
  \includegraphics[width=0.40\linewidth]{supp/bicycle20.png} \\
\hline
\end{tabular}
\caption{Failed pose estimation results on 3D Object dataset car and bike
classes. In each column, original image (left) and detection result overlaid on
top (right).}% with a bounding box and corresponding confidence score (right).}
  \label{fig:3dobject_bicycle_bad}
\end{figure*}

\section{PASCAL3D+}

We run our ensemble of NZ-WHO templates as a detector on car
and bicycle classes in PASCAL3D+ dataset  \cite{Xiang14} and present detection average precision,
average viewpoint precision, viewpoint confusion matrix and mean precision in
pose estimation. See Fig.~\ref{fig:3dobject_ap}

For each of the proposal bounding box, we assumed that there is only one object and the object 
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.24\linewidth]{supp/occlusion1.png} &
  \includegraphics[width=0.24\linewidth]{supp/occlusion1b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car1a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car1b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car3a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car3b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car5a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car5b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car6a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car6b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car7a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car7b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car10a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car10b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car16a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car16b.png}  \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car17a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car17b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car19a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car19b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car21a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car21b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car22a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car22b.png} \\
  \includegraphics[width=0.24\linewidth]{supp/pas_car18a.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18b.png} & 
  \includegraphics[width=0.24\linewidth]{supp/pas_car18c.png} &
  \includegraphics[width=0.24\linewidth]{supp/pas_car18d.png} \\
  \hline
  \end{tabular}
\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
  \label{fig:pascal3d_car_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
  \hline
  \end{tabular}
\caption{Successful detection result on PASCAL3D+ dataset car class, First tow columns are the original images and second column detection result overlaid on top. }
  \label{fig:pascal3d_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
  \hline
  \end{tabular}
\caption{Detection failure results on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
  \label{fig:pascal3d_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
  \end{tabular}
\caption{Detection Result on PASCAL3D+ dataset car class}% with a bounding box and corresponding confidence score (right).}
  \label{fig:pascal3d_bicycle_bad}
\end{figure*}
